\documentclass{article}
\usepackage[letterpaper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{amsmath, amsthm, graphicx,amssymb, enumerate}
\usepackage[nocheck]{fancyhdr}
\usepackage{url}
\fancyhead[C]{\Large\bf{Samuel Straubmuller}}
\fancyhead[L]{Statement of Purpose}
\fancyhead[R]{11/13/2024}
\fancyfoot[L]{\footnotesize The \TeX file for this document can be found here: \\
	\footnotesize\url{[link]}
}
\pagestyle{fancy}
\linespread{1.5}
\begin{document}

\par{In regards to my life, mathematics has been a constant from which I have derived insurmountable strength. I have used this strength to facilitate the learning of my peers, and it was this strength that confirmed attending graduate school for mathematics was my ultimate goal. My ultimate dream job is to be a professor of mathematics. I will stop at nothing to attain this goal, and any and all struggles along the way will strengthen my resolve to complete my degree. If admitted to this program, I will exhibit leadership, an unmatched enthusiasm for teaching, and a curious mind eager to learn.}

\par{My greatest achievement in my time as an undergraduate student is what I have been able to accomplish as a peer tutor. In this role, I assisted fellow undergraduate students of various backgrounds in their various mathematics and statistics courses. Specifically, I have tutored courses from college algebra through an introductory real analysis class. Through this role, I taught students to use study strategies to help them succeed, became a dedicated tutor for the introductory theoretical mathematics course at Winona State University, organized study sessions for exams, enabled at-risk students to effectively engage with the material of their classes, and will soon -- at the time of writing -- become certified as an academic coach. Most importantly, I learned the joy of teaching through this role. Few things compare to the joy of not only helping a student understand difficult material, but actively see their grades, happiness, and satisfaction with their college experience improve. It was through this role I saw my ideal path -- to become a professor of mathematics.}

\par{My role as a peer tutor was not my only accomplishment. While an undergraduate student I studied abroad with a group of peers in mathematics, statistics, and data science. We studied the history of mathematics in England, then visited the places we learned about. Such places include: Stonehenge, the Royal Observatory, the Christopher Wren Library, Bletchley Park, Cambridge University, the Tower of London, and Woolsthorpe Manor. This trip provided us with a unique perspective, and allowed us to reflect on the great mathematicians who came before us -- who they were, how they came to be great mathematicians, and the realization that any student could become the next great mathematician.}

\par{As an undergraduate student, I was the president of the Winona State University Math/Stat/Data Science club. Under my leadership, we unified the university's established Math/Stat club with an up-and-coming Data Science club, hosted successful social events such as a trivia night, a rock climbing night, and plan to host a fund raising competition for the Special Olympics through the Minnesota Polar Plunge. We have provided students with merchandise to allow them to show pride in mathematics, statistics, and data science. We have also engaged heavily in the community by publicly tabling at sports events, engaging with children at the Winona State University STEM carnival, and overall creating a positive relationship between people and all forms of mathematics. In addition to being the president of the Math/Stat/Data Science club, I am a member of the student advisory board to the dean of our college within the university. We have spoken to prominent leaders in the Winona area such as the mayor, the president of the university, the director of campus security, the director for career services in addition to the dean of our college. I have also participated in two mathematical competitions -- SCUDEM (an undergraduate competition in creating a mathematical model to solve a problem) and the William Lowell Putnam Competition. In April of 2024, I have been inducted into the Winona State University Mu Sigma Rho Chapter -- an honorary statistics society.}

\par{In spring of 2024, I realized I could improve my understanding of English -- so I am currently excelling in a class studying English grammar and syntax. Not only have I learned to understand the deeper structure in English, but my background in mathematics allows me to make unique connections between the English language and mathematics. For example, in English, morphemes are components of words, which in turn are components of phrases, which in turn are components of clauses. To me, this is no different than comparing different sets of numbers -- where the set of natural numbers is a subset of the integers, which in turn is a subset of the rational numbers, and so on. I am unafraid to pursue educational topics foreign to me as I yearn to learn as much as possible.}
 
\par{I have also worked on some research projects under Dr. Jacob Duncan -- particularly in modeling bat populations. While working under him, I developed a rudimentary tool using python to simulate these bat populations. Our goal was to generate boundaries between different bat roosts, and the tool produced a figure similar to a Voronoi diagram. We are currently starting a project involving mathematical synchronicity and chaos.}

\par{I have a burning desire to become a master of my discipline. If admitted into the program, I will bring not only this drive, but a mind eager to learn -- be it a day I teach, take an exam, learn about a very difficult subject, or all three. I will work tirelessly to complete my degree, teach with excellence, and persevere through the highs and lows of entering a graduate program for mathematics.}

\vspace{5mm}

Thank you, 
\vspace{5mm}

Samuel Straubmuller 
 
\end{document}